### 2018-03-27 ident/docs/draft_1.tex
change table 1

	In total, based on the above discussion, we can perturb four different model parameters ($acetate$, $k_1^{cat}$, $V_2^{max}$ and $V_3^{max}$) to obtain experimental data in silico. The 18 different parameter values used to generate experimental data are given in Table \ref{tab:pval}.	
	\begin{table}[!thbp]
		\caption{Table showing the perturbed values of all parameters used to generate experimental data in silico for testing practical identifiability of all fluxes in the small metabolic network.}
		\begin{center}				
			\begin{tabular}{llccccc}
				\hline
				Experiment Type & Perturbed Parameter & \multicolumn{5}{c}{Perturbed Values}\\
				\hline
				wild type & - & \multicolumn{5}{l}{$acetate$ = 0.1}\\
				\hline
				acetate perturbation & $acetate$ & 0.5 & 1.0 & & &\\
				\hline
				$v_1$ perturbation & $k_1^{cat}$ & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\
				\hline
				$v_2$ perturbation & $V_2^{max}$ & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\				
				\hline
				$v_3$ perturbation & $V_3^{max}$ & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\
			\end{tabular}
		\end{center}	
		\label{tab:pval}
	\end{table}

>>>>

	In total, based on the above discussion, we can perturb four different model parameters ($acetate$, $k_1^{cat}$, $V_2^{max}$ and $V_3^{max}$) to obtain experimental data in silico. The 18 different parameter values used to generate experimental data are given in Table \ref{tab:pval}.	
	\begin{table}[!thbp]
		\caption{Table showing the perturbed values of all parameters used to generate experimental data in silico for testing practical identifiability of all fluxes in the small metabolic network.}
		\begin{center}				
			\begin{tabular}{lp{3.5cm}ccccc}
				\hline
				Experiment Type & Perturbed Parameter (wild type value a.u.)& \multicolumn{5}{c}{Perturbed Values}\\
				\hline
				wild type &  &\multicolumn{5}{l}{}\\
				acetate perturbation & $acetate$ (0.1) & 0.05 & 0.09 & 0.11 & 0.5 & 1.0\\
				$v_1$ perturbation & $k_1^{cat}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\				
				$v_2$ perturbation & $V_2^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\								
				$v_3$ perturbation & $V_3^{max}$ (1) & 0.5 & 0.9 & 1.1 & 1.5 & 2.0 \\
				\hline
			\end{tabular}
		\end{center}	
		\label{tab:pval}
	\end{table}
